---
title: "Cluster"
author: "Lori Nichols"
date: "11/7/2021"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import, echo = FALSE}
pacman::p_load(tidyverse, rlist, skimr, caret, VIM, sjPlot, factoextra, NbClust, cluster, rgl, fossil)
```

```{r read, echo = FALSE}
# cluster <- read_csv("data/Measures_by_Hospital_Acute_Care_New.csv")
```

### Normalize the data using the Min-Max method

```{r normalize}
# normalize <- function(x) {
#   return ((x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE)))
# }
# 
# for(i in 2:length(cluster)) {
#   cluster[i] <- normalize(cluster[i])
# }
```

### Impute missing values using kNN imputation

```{r impute}
# kVal = floor(sqrt(nrow(cluster)))
# cluster_NAR <- cluster %>%
#   kNN(variable = 2:length(cluster), k = kVal, imp_var = FALSE)
```

```{r write, echo = FALSE}
# write_csv(cluster_NAR, "data/cluster_normalized.csv")
```

```{r seed}
set.seed(123)
```

```{r readData_All, echo = FALSE, message = FALSE, warning = FALSE}
cluster_norm <- read_csv("data/cluster_normalized.csv")

cluster_norm_vars <- cluster_norm %>%
  select(c(-"Facility.ID"))
```

```{r readData_All_Raw, echo = FALSE, message = FALSE, warning = FALSE}
cluster_norm_vars_raw <- cluster_norm %>%
  select(c(-"Facility.ID", -"Total.Performance.Score", -"Weighted.Efficiency.and.Cost.Reduction.Domain.Score", -"Unweighted.Normalized.Efficiency.and.Cost.Reduction.Domain.Score", -"Weighted.Person.and.Community.Engagement.Domain.Score", -"Unweighted.Person.and.Community.Engagement.Domain.Score", -"Weighted.Normalized.Clinical.Outcomes.Domain.Score", -"HCAHPS.Consistency.Score", -"HCAHPS.Base.Score", -"Overall.Rating.of.Hospital.Dimension.Score", -"Discharge.Information.Dimension.Score", -"Cleanliness.and.Quietness.of.Hospital.Environment.Dimension.Score", -"Communication.About.Medicines.Dimension.Score", -"Care.Transition.Dimension.Score", -"Responsiveness.of.Hospital.Staff.Dimension.Score", -"Communication.with.Doctors.Dimension.Score", -"Communication.with.Nurses.Dimension.Score", -"H_STAR_RATING.x"))
```

```{r readData_All_Summary, echo = FALSE, message = FALSE, warning = FALSE}
cluster_norm_vars_summary <- cluster_norm %>%
  select(c(-"Facility.ID")) %>%
  select(c("Total.Performance.Score", "Weighted.Efficiency.and.Cost.Reduction.Domain.Score", "Unweighted.Normalized.Efficiency.and.Cost.Reduction.Domain.Score", "Weighted.Person.and.Community.Engagement.Domain.Score", "Unweighted.Person.and.Community.Engagement.Domain.Score", "Weighted.Normalized.Clinical.Outcomes.Domain.Score", "HCAHPS.Consistency.Score", "HCAHPS.Base.Score", "Overall.Rating.of.Hospital.Dimension.Score", "Discharge.Information.Dimension.Score", "Cleanliness.and.Quietness.of.Hospital.Environment.Dimension.Score", "Communication.About.Medicines.Dimension.Score", "Care.Transition.Dimension.Score", "Responsiveness.of.Hospital.Staff.Dimension.Score", "Communication.with.Doctors.Dimension.Score", "Communication.with.Nurses.Dimension.Score", "H_STAR_RATING.x"))
```

### Calculate the Rand Index for various values of 'k'

```{r RandIndex_function, echo = FALSE, message = FALSE, warning = FALSE}
RI <- function(x, y, z) {
  km4 <- kmeans(y, centers = x, nstart = 55)
  fviz_cluster(km4, data = y, ellipse.type = c("norm"), geom = "point", palette = "Set1", ggtheme = theme_minimal())
  
  #Add cluster results to original data frame
  cluster_results <- as.data.frame(km4$cluster)
  hosp_clusters <- bind_cols(cluster_norm, cluster_results)
  
  #glimpse(cluster_results)
  #glimpse(hosp_clusters)
    
  hosp_clusters <- hosp_clusters %>%
    select(c("Facility.ID", "km4$cluster")) %>%
    rename(cluster = `km4$cluster`) %>%
    transform(Facility.ID = as.character(Facility.ID))
  #glimpse(hosp_clusters)
    
  #compare clustering results of ground truth overall star ratings
  star_ratings <- read_csv("data/Hospital_General_Information.csv")
  
  star_ratings <- star_ratings %>%
    filter(`Hospital Type` == "Acute Care Hospitals") %>%
    select(c("Facility ID", "Hospital overall rating")) %>%
    rename(Facility.ID = `Facility ID`) %>%
    rename(Star.Rating = `Hospital overall rating`) %>%
    transform(Star.Rating = as.numeric(Star.Rating))
    
  star_ratings$Facility.ID <- star_ratings$Facility.ID %>%
    trimws("left", "0")
  #glimpse(star_ratings)
    
  hosp_cluster_comparison <- full_join(hosp_clusters, star_ratings)
  #glimpse(hosp_cluster_comparison)
    
  clust_analysis <- hosp_cluster_comparison %>%
    group_by(cluster, Star.Rating) %>%
    count()
  #glimpse(clust_analysis)
    
  clust_analysis %>%
    ggplot() +
    geom_bar(mapping = aes(x = Star.Rating, y = n, fill = cluster), stat = "identity") +
    facet_wrap(~ cluster)
    
  #Use rand index to comparison compare clustering accuracy
  hosp_clust_comp <- hosp_cluster_comparison %>%
    na.omit()
  #glimpse(hosp_clust_comp)
    
  rand.index(hosp_clust_comp$Star.Rating,  hosp_clust_comp$cluster)
}
```

### Rand Index for all quality measure scores in the data table

```{r k-meansAll_RandIndex1}
kVal <- NULL
randIndex <- NULL

for(i in 2:8) {
  kVal <- list.append(kVal, i)
  randIndex <- list.append(randIndex, RI(i, cluster_norm_vars))
}

randIndexResults <- tibble(kVal = as.character(kVal), randIndex)

randIndexResults %>%
  ggplot() +
  geom_bar(mapping = aes(x = kVal, y = randIndex, fill = kVal), stat = "identity", position = "dodge")

#Low randIndex, these clusters may be useful but not an indicator of quality as defined by CMS's star ratings
#CMS uses different methodology go determine their final star ratings
```

### Rand Index for all quality measure scores minus summary scores

```{r k-meansAll_RandIndex2}
kVal <- NULL
randIndex <- NULL

for(i in 2:8) {
  kVal <- list.append(kVal, i)
  randIndex <- list.append(randIndex, RI(i, cluster_norm_vars_raw))
}

randIndexResults <- tibble(kVal = as.character(kVal), randIndex)

randIndexResults %>%
  ggplot() +
  geom_bar(mapping = aes(x = kVal, y = randIndex, fill = kVal), stat = "identity", position = "dodge")

#Low randIndex, these clusters may be useful but not an indicator of quality as defined by CMS's star ratings
#CMS uses different methodology go determine their final star ratings
```

### Rand Index for quality measure summary scores only

```{r k-meansAll_RandIndex3}
kVal <- NULL
randIndex <- NULL

for(i in 2:8) {
  kVal <- list.append(kVal, i)
  randIndex <- list.append(randIndex, RI(i, cluster_norm_vars_summary))
}

randIndexResults <- tibble(kVal = as.character(kVal), randIndex)

randIndexResults %>%
  ggplot() +
  geom_bar(mapping = aes(x = kVal, y = randIndex, fill = kVal), stat = "identity", position = "dodge")

#Low randIndex, these clusters may be useful but not an indicator of quality as defined by CMS's star ratings
#CMS uses different methodology go determine their final star ratings
```

### Clustering plot using k = 2, 4, 8

```{r k-meansAll_Clusters, fig.show = "hold", out.width = "50%", echo = TRUE, message = FALSE, warning = FALSE}
clustering <- function(x, y) {
  km4 <- kmeans(y, centers = x, nstart = 55)
  fviz_cluster(km4, data = y, ellipse.type = c("norm"), geom = "point", palette = "Set1", ggtheme = theme_minimal())
}

clustering(2, cluster_norm_vars)
clustering(4, cluster_norm_vars)
clustering(8, cluster_norm_vars)

#For quality measure scores minus summary scores
clustering(2, cluster_norm_vars_raw)
clustering(4, cluster_norm_vars_raw)
clustering(8, cluster_norm_vars_raw)

#For summary quality measure scores only
clustering(2, cluster_norm_vars_summary)
clustering(4, cluster_norm_vars_summary)
clustering(8, cluster_norm_vars_summary)

#there appear to be many correlated variables here - May need to apply dimensionality reduction or use a different clustering method to evaluate
```

### Identify which measures have the most variance using PCA

```{r PCA, message = FALSE, warning = FALSE}
#principle component analysis to see which variables are responsible for most variance
cluster.pca <- prcomp(cluster_norm_vars_summary, center = TRUE, scale. = TRUE)

fviz_eig(cluster.pca)
```

```{r PCA_Extra, echo = FALSE, message = FALSE, warning = FALSE}
#evaluate strongly correlated variables for dimensionality reduction
fviz_pca_var(cluster.pca,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE
)

cluster.var <- get_pca_var(cluster.pca)

groups <- as.data.frame(cluster.var$coord) %>%
  transform(Measures = row.names(cluster.var$coord)) %>%
  select(c(Measures, Dim.1, Dim.2)) %>%
  arrange(Dim.1, Dim.2)
```